First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-04-23 paper/paper.tex
EDSL for C code gen in paper appendix

@@

>>>>

The C backend makes use of a small EDSL for generating C code. See
Appendix B for implementation details of this ESDL.

@@

\section{EDSL for C code generation}
\begin{lstlisting}
type CCode = String
type CName = String

stmt :: CCode -> CCode
stmt = (<> ";")

cCall :: CName -> [CCode] -> CCode
cCall fnName args =
  fnName <> "(" <> intercalate ", " args <> ")"

derefPtr :: CCode -> CCode
derefPtr x = "*(" <> x <> ")"

cCast :: CCode -> CCode -> CCode
cCast toType x =
  "((" <> toType <> ")" <> x <> ")"

cIndex :: CCode -> Int -> CCode
cIndex x i = "(" <> x <> ")[" <> show i <> "]"

(!) :: CCode -> Int -> CCode
(!) = cIndex

(=:) :: CCode -> CCode -> CCode
x =: y = stmt (x <> " = " <> y)

cDecl :: CName -> CName -> CCode
cDecl cType v = stmt (cType <> " " <> v)

(#) :: CCode -> CName -> CCode
x # fieldName = x <> "." <> fieldName

macroDef :: CName -> [CName] -> [CCode] -> CCode
macroDef name args theLines =
  unlines
    [ "#define " <> name
              <> "(" <>
                intercalate ", " args
              <> ")\\"
    , "  do {\\"
    , unlines
        . map ("    "++)
        . map (++"\\")
        $ theLines
    , "  } while (0);"
    ]
\end{lstlisting}
